Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-22 supp/supp.qmd
genderize

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj)

@@

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR)

@@

We cannot know gender of authors for certainty but we can use a data driven approach to suggest the probability a particular name is of a given gender (male or female).

```{r}

# First need to get the authors first name
data2 <- data2 %>% mutate(submitting_author_firstname = str_split(submitting_author, " ") %>% map_chr(1))
# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country, simplify = FALSE)
